---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

SQaultrics is an R package that provides streamlined item important for a [Qualtrics](https://www.qualtrics.com/) survey.

## Installation

You can install SQaultrics from [GitHub](https://github.com/) with:

```{r installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github(
  "frietchr/SQaultrics"
)
```


## Disclaimer

SQualtrics was created as a class project. This course introduced students to development using R. Please see the [course website](https://sites.google.com/view/r-in-the-social-sciences) for more details. 

## Contact information

### About the Package
For Questions regarding the package please reach out to the authors:

 * Rachel Frietchen (rfrietch@masonlive.gmu.edu)
 * Oscar Medrano (omedrano@masonlive.gmu.edu)
 * Janelle Miranda (jmirand6@masonlive.gmu.edu)

### All other inquiries
Questions or comments should be directed to Shea Fyffe (sfyffe@masonlive.gmu.edu)
